Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-01 schemes.tex
Minor changes in SRLNC theory

In \ac{SRLNC}, instead of considering all the packets to create a coded
packet as in \ac{RLNC}, for this coding scheme an encoder sets more
coding coefficients to zero when generating a coded packet with the purpose
of reducing the overall processing in both encoding and decoding. In what
follows, we describe the coding scheme with a basic method to produce sparse
coded packets and later we indicate a second one, giving reference to their
implementation performance.

>>>>

In \ac{SRLNC}, instead of considering all the packets to create a coded
packet as in \ac{RLNC}, for this coding scheme an encoder sets more
coding coefficients to zero when generating a coded packet with the purpose
of reducing the overall processing. Decoding is the same as in \ac{RLNC}, but
given that the coding matrices are now sparse, we will have less operations
performed in the decoding process. Recoding, although theoreticaly possible,
is omitted in practical systems since it is too complex to keep packets sparse
after recoding [\textbf{reference}]. In what follows, we
describe the coding scheme with a basic method to produce sparse coded
packets and later we indicate a second one, giving reference to their
implementation performance.
